---
title: "Leaflet Assignment"
author: "Haiko Didzoleit"
date: "28 November 2016"
output: html_document
always_allow_html: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This map is used for the coursera assignment "Developing data products" week 2. 
To remember the technical failure the topic used is the Fukushima reactor plant that created a massive radiation failure in japan and wide parts of east asia coastial regions for hundreds of years. 


```{r, eval=FALSE, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map
```

```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()

```

## Creating the basic maps with marker on the powerplant

```{r, eval=FALSE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=37.422535, lng=141.034000, 
             popup="Tepco Power plant")
my_map
```

## Additionally mark the areas of the radioactive contaminated area which was designated by Greenpeace on 2015

```{r}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=37.422035, lng=141.034000, 
             popup="Tepco Power plant")
my_map

md_cities <- data.frame(name = c("Baltimore", "Frederick", "Rockville", "Gaithersburg", 
                                 "Bowie", "Hagerstown", "Annapolis"),
                        pop = c(20000, 10000, 8000, 4000, 1500, 1000, 400),
                        lat = c(37.422535, 37.422535, 37.422535, 37.422535, 37.422535, 37.422535, 37.422535),
                        lng = c(141.034000, 141.034000, 141.034000, 141.034000, 141.034000,141.034000,141.034000),
                        col = c("lightgreen","yellow","orange","darkorange","red","darkred","black")
)
md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(lat = md_cities$lat, lng = md_cities$lng, weight = 1, radius = md_cities$pop, color = md_cities$col) %>%
  addLegend(labels= c("low radiation", "", "", "medium radiation", "high radiation", "extreme radiation", "core location"), color = md_cities$col)
  
```
Thank you for observing my scheme for this course. 
And mind the danger of nuclear powerplants and the radiation

## Conclusion

For more details about the leaflet package for R 
visit http://rstudio.github.io/leaflet/.

